\documentclass[12pt]{article}

\pagestyle{empty}
\setcounter{secnumdepth}{0}

\topmargin=0cm
\oddsidemargin=0cm
\textheight=22.0cm
\textwidth=16cm
\parindent=0cm
\parskip=0.15cm
\topskip=0truecm
\raggedbottom
\abovedisplayskip=3mm
\belowdisplayskip=3mm
\abovedisplayshortskip=0mm
\belowdisplayshortskip=2mm
\normalbaselineskip=12pt
\normalbaselines

\begin{document}

\vspace*{0.2in}
\centerline{\bf\Large Diary}

\vspace*{0.2in}
\centerline{\bf\Large Name: Mona Shayvard.  Student ID: 40061450.}

\vspace*{0.2in}
\centerline{\bf\Large Team PK-B}

\vspace*{0.2in}
\centerline{\bf\Large 08 January 2019}

\section{Iteration 1}
{\bf Date:} 15 January 2020. \\
{\bf Start Time:} 7:15PM. \\
{\bf End Time:} 8:45PM. \\
{\bf Duration:} 90 minutes. \\
{\bf Who:} Pavel Balan, Ivan Garzon, Ki Ho Lee, Nian Liu, Anthony Menard-Gill, \\
\hspace{10mm} Micheal Naccache, Ashish Saha, Myriam Tayah, Mona Shayvard. \\
{\bf Where:} Room H-831. \\
{\bf Activities:} It was the first time I met my team mates. We assigned different roles organizer, coders and documenters for the first iteration. We decided to do some tutorials about Latex and JUnit also setting Trello to track our progress. With the help of TA we did a bit discussion about the first phase. \\
{\bf Outcomes:} I got to know my teammates, and I was added to the Slack room; Roles are decided as follows: \\
Organizer: Pavel Balan \\
Documentors: Ivan Garzon, Anthony Menard-Gill, Micheal Naccache, Ashish Saha and Me \\
Coders: Ki Ho Lee, Nian Liu and Myriam Tayah \\
\vspace*{0.2in} \\
{\bf Date:} 16 January 2020. \\
{\bf Start Time:} 8:30PM. \\
{\bf End Time:} 9:20PM. \\
{\bf Duration:} 50 minutes. \\
{\bf Who:} Pavel Balan, Ivan Garzon, Ki Ho Lee, Nian Liu, Anthony Menard-Gill, \\
\hspace{10mm} Micheal Naccache, Ashish Saha, Myriam Tayah, Mona Shayvard. \\
{\bf Where:} Room H-523. \\
{\bf Activities:} TA talked about  use cases diagrams and descriptions, also domain models. The we discussed the possible use cases for the Kakuro game in our team also with the TA and we could make a draft list for our user cases \\
{\bf Outcomes:} Gained more knowledge about domain models, use cases and relate them to our project.\\

{\bf Date:} 19 January 2020. \\
{\bf Start Time:} 4 PM. \\
{\bf End Time:} 5 PM. \\
{\bf Duration:} 60 minutes. \\
{\bf Who:} Mona Shayvard. \\
{\bf Where:} Home. \\
{\bf Activities:} I went through the lectures and project documentations. Tried to learn more about the user cases according to the TA's notes and some internet search. \\
{\bf Outcomes:} Improved my knowledge about the project needs. 
\vspace*{0.2in} \\


{\bf Date:} 20 January 2020. \\
{\bf Start Time:} 4:40PM. \\
{\bf End Time:} 5:45PM. \\
{\bf Duration:} 65 minutes. \\
{\bf Who:} Ivan Garzon, Anthony Menard-Gill, \\
\hspace{10mm} Micheal Naccache, Ashish Saha,  Mona Shayvard. \\
{\bf Where:} Technoloy Sandbox. \\
{\bf Activities:} It was a meeting for documentors and we discussed more about the possible user cases, domain models, relations  and we define 10 user cases which among them we will implement 3.   \\
{\bf Outcomes:} Have a better list of user cases, understood more about the relations between user cases, discussed about the roles and responsibilities: Me, Ivan and ANthony are going to write the user cases, Ashish will write Section 1-3, and Micheal will write Section 5-7. We still have some ambiguity about Data Dictionary and  Non-Functional Constraints and we suppose to ask the prof or the TA. \\
%\section{Iteration 2}

%\section{Iteration 3}

\end{document}